Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-12 paper/uist_2016/paper.tex
fix some typos

There are some inherent limitations to Rewind due to today's technologies. Location data is imperfect, and often can hop around the map, showing the user places they may have never been. But even more important is the limits to how realistic a Rewind can truly be. People and conversations, which are what we think about often, can't be shown in Rewinds without some additional recording device. Therefore, while Rewind does not recreate the exact memory, it's more of a proxy for what environment where the memory occurs.

@@

Besides visuals, a salient part of a memory is in the sounds from the past. This can be replicated through a number of styles: the pitter-patter of footsteps or sound of driving through the streets (mode of transportation can be detected purely from geolocation data \cite{zheng2008learning}), the whistle of the winds or thunderstorms at night, and even sounds based on geographical features like when the user was near water or by a outdoor market. van Djick explains, ``One memory rarely encompasses all sensory modes, because we tend to remember by selecting particular ones. For instance, we may recall a mood, locale or era through a particular smell (such as the smell of apple pie in the oven triggering the image of your mother's kitchen on Saturday afternoons), or we may remember a person by his nasal voice or twinkling eyes'' \cite{van2007mediated} (pg. 20). Audio and visuals combined can enrich the experience, as Rewind uses environmental data such as weather information or the season to incorporate other sensory modes. By leveraging environmental sensory data, users may be stimulated to recall something that may have been forgotten otherwise, and this information makes the experience feel more real.

>>>>

There are some inherent limitations to Rewind due to today's technologies. Location data is imperfect, and often can hop around the map, showing the user places they may have never been. But even more important is the limits to how realistic a Rewind can truly be. People and conversations, which are what we think about often, can't be shown in Rewinds without some additional recording device. Therefore, while Rewind does not recreate the exact memory, it's a proxy for what environment where the memory occurs.

@@

Besides visuals, a salient part of a memory is in the sounds from the past. This can be replicated through a number of styles: the pitter-patter of footsteps or sound of driving through the streets (mode of transportation can be detected purely from geolocation data \cite{zheng2008learning}), the whistle of the winds or thunderstorms at night, and even sounds based on geographical features like when the user was near water or by a outdoor market. van Dijck explains, ``One memory rarely encompasses all sensory modes, because we tend to remember by selecting particular ones. For instance, we may recall a mood, locale or era through a particular smell (such as the smell of apple pie in the oven triggering the image of your mother's kitchen on Saturday afternoons), or we may remember a person by his nasal voice or twinkling eyes'' \cite{van2007mediated} (pg. 20). Audio and visuals combined can enrich the experience, as Rewind uses environmental data such as weather information or the season to incorporate other sensory modes. By leveraging environmental sensory data, users may be stimulated to recall something that may have been forgotten otherwise, and this information makes the experience feel more real.
